Modeling Bandwagoning and Hype in the MLB

### 2020-08-23 Paper_Outline.Rmd
Updated plots for paper outline

fig3_dat %>%
  ggplot(aes(x = googlehits)) + 
  geom_histogram(bins = 30,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(main = "Google Trend Hits", x = "Google Hits")

@@

```{r}
fig3_dat %>%
  ggplot(aes(x = log(googlehits))) + 
  geom_histogram(bins = 10,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(main = "Google Trend Hits", x = "Google Hits")
```

@@

>>>>

fig3_dat %>%
  ggplot(aes(x = googlehits)) + 
  geom_histogram(bins = 30,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(title = "Google Trend Hits", x = "Google Hits")

@@

```{r}
fig3_dat %>%
  ggplot(aes(x = log(googlehits))) + 
  geom_histogram(bins = 10,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(title = "Google Trend Hits", x = "Google Hits")
```

@@

```{r}
fig4_dat <- read.csv("plotting_data.csv") %>%
  mutate(date = as.Date(date),
         month = as.month(month))

# giants - quantile normalized hits plot for last 5 years
fig4_dat %>%
  filter(team == "San Francisco Giants",
         date <= as.Date("2020-07-01") & date >= as.Date("2015-07-01")) %>%
  ggplot(aes(x = date, y = qn_ghits)) +
  geom_line(col = "darkorange") +
  theme_minimal() +
  labs(title = "San Francisco Giants")

# giants - monthly average hits over ALL years with phases
fig4_dat %>%
  filter(team == "San Francisco Giants") %>% 
  group_by(month) %>%
  summarise(monthly_avg = mean(googlehits)) %>%
  ggplot(aes(x = month, y = monthly_avg)) +
  geom_line(col = "darkorange") +
  xlim(1,12) + 
  geom_vline(xintercept = c(4,10), linetype = "dashed", color = "black") + 
  geom_text(aes(x=2, y=7, label = "Off-Season")) +
  geom_text(aes(x=4, y=7, label = "Opening Day\n"), angle = 90) + 
  geom_text(aes(x=7, y=7, label = "Season")) + 
  geom_text(aes(x=10, y=7, label = "Post-Season\n"), angle = 90) + 
  geom_text(aes(x=11.5, y=7, label = "Off-Season"))
  # geom_vline(xintercept = 10, linetype = "dashed", color = "black") + 
  # geom_vline
```

```{r}
# padres
fig4_dat %>%
  filter(team == "San Diego Padres") %>%
  ggplot(aes(x = date, y = googlehits)) +
  geom_line(col = "tan4") +
  theme_minimal() +
  labs(title = "San Diego Padres")
```
